\section{Introduction}

In the last two decades, image-detection systems have seen practical applications within various domains [1]-[8], but only recently has there been an apparent shift from heuristic-driven systems to machine-learning ones. Since the advancement of the \glspl{cnn} from handwritten characters [9] to object detection [10] on the ImageNet dataset, we have seen increasing interest in improving the \gls{cnn}.
[1]	S. S. Tsai, D. M. Chen, V. Chandrasekhar, G. Takacs, N.-M. Cheung, R. Vedantham, R. Grzeszczuk, and B. Girod, “Mobile product recognition.,” ACM Multimedia, 2010.
[2]	B. Girod, V. Chandrasekhar, D. Chen, N.-M. Cheung, R. Grzeszczuk, Y. Reznik, G. Takacs, S. Tsai, and R. Vedantham, “Mobile Visual Search,” IEEE Signal Process. Mag., vol. 28, no. 4, pp. 61–76, 2011.
[3]	G. Takacs, V. Chandrasekhar, N. Gelfand, Y. Xiong, W.-C. Chen, T. Bismpigiannis, R. Grzeszczuk, K. Pulli, and B. Girod, “Outdoors augmented reality on mobile phone using loxel-based visual feature organization.,” Multimedia Information Retrieval, 2008.
[4]	J. Sivic and A. Zisserman, “Video Google - A Text Retrieval Approach to Object Matching in Videos.,” ICCV, 2003.
[5]	D. G. Lowe, “Distinctive Image Features from Scale-Invariant Keypoints.,” Int J Comput Vis, vol. 60, no. 2, pp. 91–110, 2004.
[6]	H. Bay, A. Ess, T. Tuytelaars, and L. J. Van Gool, “Speeded-Up Robust Features (SURF).,” Computer Vision and Image Understanding, 2008.
[7]	C. M. Jin, Z. Omar, and M. H. Jaward, “A mobile application of American sign language translation via image processing algorithms,” presented at the 2016 IEEE Region 10 Symposium (TENSYMP), 2016, pp. 104–109.
[8]	A. W. M. Smeulders, M. Worring, S. Santini, A. Gupta, and R. C. Jain, “Content-Based Image Retrieval at the End of the Early Years.,” IEEE Trans. Pattern Anal. Mach. Intell., 2000.
[9]	Y. LeCun, L. Bottou, Y. Bengio, and P. Haffner, “Gradient-based learning applied to document recognition,” Proceedings of the IEEE, vol. 86, no. 11, pp. 2278–2324, 1998.
[10]	A. Krizhevsky, I. Sutskever, and G. E. Hinton, “ImageNet Classification with Deep Convolutional Neural Networks.,” NIPS, 2012.
